---
title: "Homework 1"
author: "Jessie Merrifield"
date: 2023-09-23
output: github_document
---


# Problem 1



## Starting out with loading libraries and the dataset for Problem 1.

```{r, message=FALSE}
library(moderndive)
library(tidyverse)

data("early_january_weather")
```




## Describing the data with a summary, the number of rows, the number of columns, and the mean of the variable "temp"

```{r descriptive}
summary(early_january_weather)

nrow(early_january_weather)

ncol(early_january_weather)

mean(early_january_weather$temp)

early_january_weather %>% 
  pull(temp) %>%  
  mean()
```



## Scatterplot for temp vs. time_hour, color by variable humid 

```{r scatterplot}

P1_scatter<-ggplot(data = early_january_weather,
                   aes(x=time_hour, y=temp, color=humid))+
  geom_point()

ggsave("scatter_plot_P1.pdf", height = 4, width = 6)

print(P1_scatter)

```


There seems to be an overall positive relationship between temp and time_hour with
temp appearing to increase with time_hour. There is not a clear relationship between humidity
and temp and time_hour. 






# Problem 2


## Creating a dataframe

```{r dataframe}
Problem2_df = tibble(
  vec_numeric = rnorm(10),
  vec_char = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
  vec_logical = vec_numeric>0,
  vec_factor = factor(c("1", "1", "1", "2", "2", "2", "3", "3", "3","3"))
)

```




## Taking the means of each vector in Problem2_df. 
The logical and numeric variables worked while the character and factor variables did not. 

```{r means}
Problem2_df %>% 
  pull(vec_char) %>% 
  mean()

Problem2_df %>% 
  pull(vec_factor) %>% 
  mean()


Problem2_df %>% 
  pull(vec_logical) %>% 
  mean()

Problem2_df %>% 
  pull(vec_numeric) %>% 
  mean()

```
Warning: argument is not numeric or logical: returning NA[1] NA










## Converting variables to numeric. 

All of the variables were able to be converted to numeric, which is probably due to the fact that I had used numbers for the character and factor vectors. It is interesting that the logical vector that originally used TRUE and FALSE is now using 1 and 0. However, this explains why the logical vector was able to be used for the mean function as the data seems
to be stored as a numeric binary rather than the words "TRUE" and "FALSE."


```{r, results='hide'}
Problem2_df %>% 
  pull(vec_logical) %>% 
  as.numeric()

Problem2_df %>% 
  pull(vec_char) %>% 
  as.numeric()

Problem2_df %>% 
  pull(vec_factor) %>% 
  as.numeric()
```

